\section{Distributed Systems}

\quad{} 
 When we speak about an distributed system, theres an list of things that we need to think of, in order to understand the main characteristics that they share in computational terms. Without further abuse, the main characterist that more explain the nature of an distributed system are:
  Concurrency, this stands for an system that can handle multiple proccesses that run simultaneously, this of course in different machines that in an certain time align with each other to reach an common goal.
  Scalability, relatively to this precise characteristic, we know that if we have an distributed network, we must ensure that in an certain way we can scalate the system. This scalability can either be vertical(hardware) or either horizontal(number of instances), which has the goal of increasing the performance of an certain system.
  Fault-tolerant, this is much of importance, because in some distributed systems it becomes incommensurable to not have counter-measures to faults. This faults could either be:
  Transient faults, it occurs when there is an temporary fault that occur due to a sudden and brief disruption in the system.
  Intermittent faults, which occurs sporadically and unpredictably, making them difficult to diagnose and detect.
  Partial Faults, this one occurs when an partial part of the components fails, but the system still works without that failure of the component.
  Byzantine Faults, finally it occurs when an component behaves malicously or incorrectly, this are the most severe and complex faults in an distributed system.
  There are more faults but those are what we as an group think are more relevant.
  Coming back to the characteristics of an distributed system we also have transparency, which stands for an user not having the capability of knowing which processes are involved in an distributed system that he is interacting with.
  Heterogeneity, an distributed system may have different resources, behing heteregeneous, means that it can have different pieces and still give the same importance for each of them and possibily dont even knowing his importance and magnitude.
  Resource sharing, an distributed system allows users to share resources, shuch as data, processing power, etc...
  There are a lot of characteristics, and every characteristic may have an specific naming for an more specific situation, but those are the main characteristics and they do represent well how should an distributed system behave.
\quad Our solution is related to Distributed Systems due to the fact that we are aiming for it to be one. By definition, a Distributed System consists of a set of autonomous machines that are connected to the same network with different components that interact with each other, communicate and coordinate their actions using the exchange of messages as a resource.
  Therefore, our objective with this project is that if a microsystem fails, there is no compromise of the whole system. Furthermore, we intend that all components be able to communicate with each other, by exchanging messages as is done in a distributed system.